Navigating to a greener Europe with 24/7 hourly clean electricity procurement

### 2023-04-16 manuscript/sections/results.tex
add uncovering mechanisms section

\cref{fig:10-2025-DEPL-p3-4plots} shows results for the two selected regions: Germany and Poland. Germany is selected as it the largest electricity consumer in Europe and it is well interconnected to regions with clean electrcity grids, such as France and Denmark. 
Poland -- a country with  historic dependency on domestic coal resources, resistance from the coal industry and lack of governmental support for renewable energy -- is selected for a contrast. To keep other factors constant, the same 10\% share of \gls{ci} consumers is set to participate in voluntary clean electricity procurement.%
\footnote{10\% participation rate of \gls{ci} sector yields load of 3.8~GW in Germany and 1.1~GW in Poland.}

@@

\vspace{5pt}
\begin{res}
    The difference in impact that 24/7 CFE procurement and 100\% annual matching policies have on system decarbonisation amplifies between 2025 and 2030 with a cleaner state of local grids.
\end{res}

\vspace{5pt}
\begin{res}
    24/7 procurement reduces the needs for flexibility in the rest of the system.
\end{res}

text on results 8 and 9

@@

text on result 10

>>>>

\cref{fig:10-2025-DEPL-p3-4plots} shows results for the two selected regions: Germany and Poland. Germany is selected as it the largest electricity consumer in Europe and it is well interconnected to regions with clean electrcity grids, such as France and Denmark. 
Poland—a country with  historic dependency on domestic coal resources, resistance from the coal industry and lack of governmental support for renewable energy—is selected for a contrast. To keep other factors constant, the same 10\% share of \gls{ci} consumers is set to participate in voluntary clean electricity procurement.%
\footnote{10\% participation rate of \gls{ci} sector yields load of 3.8~GW in Germany and 1.1~GW in Poland.}

@@

\vspace{5pt}
\begin{res}
    The difference in impact that 24/7 CFE procurement and 100\% annual matching policies have on system decarbonisation amplifies with a cleaner state of local grids.
\end{res}

\vspace{5pt}
\begin{res}
    24/7 CFE procurement reduces the needs for flexibility in the rest of the system.
\end{res}

As illustrated in Figures \ref{fig:10-2025-IE-p1-zone_emissions}, \ref{fig:10-2025-DE-p3-zone_emissions}, \ref{fig:10-2025-PL-p3-zone_emissions} and \ref{fig:10-2030-IE-p1-zone_emissions}, voluntary commitments to 24/7 clean energy procurement result in a considerable reduction of \co emissions in local electricity grids. 
In this section, we delve deeper into the underlying mechanisms responsible for these observed reductions aiming to enhance our understanding of the complex interplay between clean energy procurement and emissions reduction at the system level.

The reduction of system-wide emissions can be attributed to two primary mechanism driven by the dynamics of clean energy procurement and grid-supplied generation.

First, the timing mechanism, concerns the alignment of clean electricity supply with electricity demand of participating consumers. When a share of electricity consumption in a given region is closely alligned with CFE supply, the need for backup dispatchable generation is reduced. This effect can reduce utilization of fossil-based peak generators, such as \gls{ocgt} power plants, particularly during periods when wind and solar resources are scarce.

Second, the volume mechanism, pertains to the overall quantity of clean electricity generated by procured resources. 
The excess clean electricity sold to the grid can displace the emitting grid generators or reduce the need of electricity imports from the neighbouring regions.
The decarbonisation effect depends on the composition of the 24/7 portfolio, the volume of excess generation that is sold to the grid and the generation (and import) mix in the local zone when the excess electricity is sold.

In the following, we do an experiment to isolate the volume from the profile mechanism. 
We aim to attribute the reduction of \co emissions in a local zone either to the excess electricity or to the better alignment of procured generation with \gls{ci} consumers' demand.
In the experiment, we rerun the optimization with setting the rigt-hand side of the constraint \textit{TODO CORRECT REF} to zero, so that only the profile mechanism is present. The difference in emissions to the case with excess allowed, we assign to the volume mechanism.

\cref{fig:10-profile-volume.pdf} shows the results of the experiment -- the reduction of emissions in a local zone in Mt\co per year if 10\% of \gls{ci} consumers commit to 24/7 hourly procurement with 100\% CFE target with isolated contributions of the profile and volume mechanisms.
In other words, \cref{fig:10-profile-volume.pdf} attributes the difference between emissions in the \textit{reference} and the \textit{100\%} 24/7 CFE cases presented  Figures \ref{fig:10-2025-IE-p1-zone_emissions}, \ref{fig:10-2025-DE-p3-zone_emissions}, \ref{fig:10-2025-PL-p3-zone_emissions} and \ref{fig:10-2030-IE-p1-zone_emissions} (right columns) to the two decarbonisation mechanisms. 
The x-axis of the \cref{fig:10-profile-volume.pdf} lists different states of electricity grids where consumers following 24/7 approach can be located: a combination of four zones and two modelled years yields eight 'background' systems.

Two observations in (\cref{fig:10-profile-volume.pdf}) follow intuition: (i) the impact on local zone emissions of 24/7 hourly CFE procurement policy is notably different in absolute numbers (Mt\co per year) depending on \gls{ci} consumers' location, and (ii) the decarbonisation effect of voluntary clean electricity procurement reduces over time since electricity mix in all modelled zones becomes cleaner due to tightening of \gls{necp}s and decomissioning of old emitting power plant fleet. 
Isolation of the profile and volume mechanisms offers news insights. First, both mechanisms contribute to the system decarbonisation. Second, the cases of Germany and Poland 2030 show that the impact of both mechanisms is also present with the cleaner states of the grid in 2030.

The economic intuition suggests that self-cannibalisation effect of non-dispatchable generators, such as wind and solar, can decrease the impact of clean energy procurement on system-level decarbonisation.  
\cref{fig:10-hourly-annual.pdf} provides a nuanced view on this point.
The figure presents the \textit{additional} reduction of \co emissions in a local zone driven by the 100\% 24/7 hourly matching with clean electricity over the 100\% annual (volumetric) matching policy.
In other words, \cref{fig:10-hourly-annual.pdf} illustrates proportional impact of the emissions reduction acvieved by the \textit{RES100\%} and the \textit{100\%} 24/7 CFE policies presented in Figures \ref{fig:10-2025-IE-p1-zone_emissions}, \ref{fig:10-2025-DE-p3-zone_emissions}, \ref{fig:10-2025-PL-p3-zone_emissions} and \ref{fig:10-2030-IE-p1-zone_emissions} (left and right columns), and gives an intuition how the impact changes between 2025 and 2030.

A prominent observation in \cref{fig:10-hourly-annual.pdf} is that 100\% annual matching (or any other volumetric-based matching policy) has a proportionally smaller effect on a system decarbonisation than 24/7 hourly matching in 2030 compared to 2025. 
This result is driven by the diminishing value of each additional megawatt of capacity of non-dispatchable generators, i.e., self-cannibalisation of solar and wind generators. 
The 24/7 hourly CFE matching have a stronger decarbonisation impact in a cleaner systems due to (i) the profile mechanism, (ii) the volume mechanism, since the procured resources have a more diverse portfolio including battery storage, long-duration energy storage or advanced clean firm technologies that allow for having clean electricity available in periods when system-wide wind and solar generation is scarce.

@@
